---
title: "Search"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Search}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(WikidataR)
```

In this article you will learn how to find items and knowledge on Wikidata via 
the WikidataR functions.

### Search Wikidata to see if an item exists (example: pharmaceuticals)
For cases where you don't already know the QID of an item or the PID of a property, you can search wikidata by name. Note that some search terms will return multiple possible items. You can also specify a language (defaults to English).

```{r finditem}
find_item("Paracetamol")
```


```{r}
find_property("medical condition treated")
```

Which returns the lists: 

```
    acetaminophen (Q57055) - common drug for pain and fever  
    Paracetamol (Q36716177) - scientific article published on July 1980  
    Paracetamol (Q54982056) - musical group  
    ...
```

and
```
    medical condition treated (P2175) - disease that this pharmaceutical drug, procedure, or therapy is used to treat 
```
Elements within those lists include basic information from wikidata (ID, description, labels). The QID or PID can then be used to get the full data for the item (see below).

