---
title: "Query Wikidata with Complex Searches in SPARQL"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Query Wikidata with Complex Searches in SPARQL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(WikidataR)
```
In this example, we search Wikidata for any items that are an "instance of" ([P31](https://www.wikidata.org/wiki/Property:P31)) "film" ([Q11424](https://www.wikidata.org/wiki/Q11424)) that has the label "The Cabin in the Woods" ([Q45394](https://www.wikidata.org/wiki/Q45394)), and ask for the item's genres ([P136](https://www.wikidata.org/wiki/Property:P136)).

``` r
query_wikidata('SELECT DISTINCT
  ?genre ?genreLabel
WHERE {
  ?film wdt:P31 wd:Q11424.
  ?film rdfs:label "The Cabin in the Woods"@en.
  ?film wdt:P136 ?genre.
  SERVICE wikibase:label { bd:serviceParam wikibase:language "en". }
}')
```
Which returns a tibble:
```
    # A tibble: 6 x 2
      genre                                   genreLabel          
      <chr>                                   <chr>               
    1 http://www.wikidata.org/entity/Q3072049 zombie film         
    2 http://www.wikidata.org/entity/Q471839  science fiction film
    3 http://www.wikidata.org/entity/Q859369  comedy-drama        
    4 http://www.wikidata.org/entity/Q1342372 monster film        
    5 http://www.wikidata.org/entity/Q853630  slasher film        
    6 http://www.wikidata.org/entity/Q224700  comedy horror    
```

For more example SPARQL queries, see [this page](https://www.wikidata.org/wiki/Wikidata:SPARQL_query_service/queries/examples) on [Wikidata](https://www.wikidata.org/wiki/Wikidata:Main_Page).


## Links for learning SPARQL  

-   [A beginner-friendly course for SPARQL](https://www.wikidata.org/wiki/Wikidata:A_beginner-friendly_course_for_SPARQL)
-   Building a SPARQL query: [Museums on Instagram](https://www.wikidata.org/wiki/Help:SPARQL/Building_a_query/Museums_on_Instagram)
-   [SPARQL Query Examples](https://www.wikidata.org/wiki/Wikidata:SPARQL_query_service/queries/examples) for WDQS
-   [Using SPARQL to access Linked Open Data](https://programminghistorian.org/lessons/graph-databases-and-SPARQL) by Matthew Lincoln
-   Interesting or illustrative [SPARQL queries](https://www.wikidata.org/wiki/Wikidata:SPARQL_query_service/queries) for Wikidata
-   Wikidata [2016 SPARQL Workshop](https://www.wikidata.org/wiki/Wikidata:SPARQL_query_service/2016_SPARQL_Workshop)
-   [Wikidata SPARQL Query video tutorial](https://www.youtube.com/watch?v=1jHoUkj_mKw) by Navino Evans
-   *[Learning SPARQL](http://www.learningsparql.com/)* by Bob DuCharme
-   [WDQS User Manual](https://www.mediawiki.org/wiki/Wikidata_query_service/User_Manual)
