---
title: "Write New Knowledge to Wikidata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Write New Knowledge to Wikidata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(WikidataR)
```

In this example we'll write directly to wikidata via the [QuickStatements](https://tools.wmflabs.org/quickstatements) format.

``` r
write_wikidata(items      = c("Q4115189","Q13406268"),
               properties = "author",
               values     = c("Q762","Q41406"),
               format     = "api",
               api.username = "myusername", # Enter your Wikimedia username here
               api.token  = "" #REDACTED# Find yours from https://tools.wmflabs.org/quickstatements/#/user
               )
```
Results in the statements being directly added to wikidata under your username via the API.  
> The Mona Lisa (Q12418) has the Creator (P170) of Leonardo da Vinci (Q762)  
> The Scream (Q471379) has the Creator (P170) of Edvard Munch (Q41406)  

Alternatively, you can print via <code>format=tibble</code> and paste into the [QuickStatements](https://tools.wmflabs.org/quickstatements) website.

### Combining all of the above (example: journal articles)
The example below finds all articles in a journal, works out the URL for their peer reviews, and writes those URLs into those articles' wikidata items.
``` r
sparql_query <- 'SELECT ?Article ?ArticleLabel ?JLabel ?T ?peer_review_URL WHERE {
  SERVICE wikibase:label { bd:serviceParam wikibase:language "[AUTO_LANGUAGE],en". }
  ?Article wdt:P1433 wd:Q24657325.
  OPTIONAL { ?Article wdt:P1433 ?J. }
  OPTIONAL { ?Article wdt:P1476 ?T. }
  OPTIONAL { ?Article wdt:P7347 ?peer_review_URL. }}
LIMIT 10000'
articles.qr <- as_tibble(query_wikidata(sparql_query))
articles.qr <- articles.qr[articles.qr$peer_review_URL=="",] #omit those with review URLs listed
review.URLs <- paste0('https://en.wikiversity.org/wiki/Talk:',
                      articles.qr$JLabel,
                      "/",
                      articles.qr$T
                     )
review.URLs <- gsub(" ","_",review.URLs)

write_wikidata(items      = sapply(sapply(articles.qr$Article,pattern = "/",stringr::str_split),tail,1),
               properties = "Peer review URL",
               values     = review.URLs,
               format     = "tibble",
               )
                  
write_wikidata(items        = sapply(sapply(articles.qr$Article,pattern = "/",stringr::str_split),tail,1),
               properties   = "Peer review URL",
               values       = review.URLs,
               format       = "api",
               api.username = "myusername", 
               api.token    = , #REDACTED# Find yours from https://tools.wmflabs.org/quickstatements/#/user
               )
```
